Light versus dark in strong-lens galaxies: Dark matter haloes that are rounder than their stars

### 2015-09-22 shapes/paper.tex
Tiny fix

@@

Throughout this work we consider a fixed, flat cosmological model with matter density $\Omega_{m} = 0.28$, dark energy density $\Omega_{\Lambda} = 0.72$, and the inverse Hubble constant $H_{0}^{-1} = 13.7$ Gyr.

>>>>

Throughout this work we assume a flat $\Lambda$CDM model with matter density $\Omega_{m} = 0.28$, dark energy density $\Omega_{\Lambda} = 0.72$, and inverse Hubble constant $H_{0}^{-1} = 13.7$ Gyr.

@@
